Word learning at the semantics pragmatics interface

### 2020-04-14 paper/supplementary_material.Rmd
add reference to model files to supplement

All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository (file xxxxx). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned. The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.

@@

The *integration model* in this section differs from the integration model in the **Prediction Section** only in that the parameter distributions are now additionally informed by the data from Experiment 3. Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the *integration* model. Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2. In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data. That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that younger children are more sensitive to the common ground manipulation and there is less developmental change. The code to run the model can be found in the associated online repository (file: xxxxxxx). Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.

@@

To estimate $\phi$ as well as the other parameters, we make use of all the available data. The model code can be found in the associated online repository (file: xxxxxxx). The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A. It suggests that the mutual exclusivity inference is weighted as slightly more important compared to the common ground inference.

@@

For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3. Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter. Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity inference with age.

>>>>

All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned. The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.

@@

The *integration model* in this section differs from the integration model in the **Prediction Section** only in that the parameter distributions are now additionally informed by the data from Experiment 3. Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the *integration* model. Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2. In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data. That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that younger children are more sensitive to the common ground manipulation and there is less developmental change. The code to run the model can be found in the associated online repository (file: `webppl/explanation_integration_model.wppl`). Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.

@@

To estimate $\phi$ as well as the other parameters, we make use of all the available data. The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`). The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A. It suggests that the mutual exclusivity inference is weighted as slightly more important compared to the common ground inference.

@@

For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3. The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`). Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter. Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity inference with age.
